---
title: "Analysis of @WeRateDogs tweets"
author: "Parth Thakur"
date: "11 September 2018"
output:
  html_document: default
---
<a href=https://github.com/ParthThakur/Wrangling-and-Analyzing-WeRateDogs-twitter-archive>
Github</a>

```{r setup, include=FALSE}
# R Markdown options
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

```{r}
# import required libraries.
library(ggplot2)
library(dplyr)
library(gridExtra)
```

Our dataset has data for over 1500 tweets by @WeRateDogs.

@WeRateDogs is a twitter account that rates dogs on the internet on a scale of 
10. But all the dogs are rated above 10. Why? 
<a href=https://knowyourmeme.com/memes/theyre-good-dogs-brent>Because they are 
good dogs, Brent.</a>

This dataset originally contained over 2500 tweets. I used data wrangling 
techniques to filter out data not needed for this analysis. The wrangling 
process can be found <a href=https://parththakur.page.link/wrangling>here.</a>


```{r, Read Data}
# Read cleaned dataset.
df <- read.csv("twitter_archive_master.csv", stringsAsFactors=FALSE)
rownames(df) <- df$tweet_id
df$tweet_id <- NULL
df$dog_breed <- factor(df$dog_breed)
df$dog_name <- factor(df$dog_name)
```

The data in our dataset looks something like this:

```{r, Show Data}
head(df)
```


Let me start by checking some descriptive statistics on the important columns.

```{r, Descriptive statistics}
#Descriptive statistics on the important columns.
summary(subset(df, 
               select=-c(timestamp, text, jpg_url, breed_confidence)))
```

There are a few that things that become apparent here.

1. The five most common dog names are:
    - Cooper
    - Lucy
    - Charlie
    - Oliver
    - Tucker
    
2. The five most common dog breeds are:
    - Golden Retriever
    - Labrador Retriever
    - Pembroke
    - Chihuahua
    - Pug
    
3. There are a few outliers on in both rating numerator, rating denominator. 
   Most interestingly, there are a few ratings below 10.
   
4. Least amount of retweets are 12, while the maximum is 84,113.

5. Least amount of favourites is 80, while the maximum is 161,869.

```{r, read again}
# To get the values for each name and breed in the last chart, dog_name and 
# dog_breed had to be factors. But going forward, I want them to be character 
# class. As R doesn't provide a simple way to change factors to character, reading
# the dataset back is the fastest and the most simple way.

df <- read.csv("twitter_archive_master.csv", stringsAsFactors=FALSE)
rownames(df) <- df$tweet_id
df$tweet_id <- NULL
df$timestamp <- as.POSIXct(df$timestamp)
```


```{r, create breed factor}
# Create a factor variable to indicate top 5 most common dog breeds. The 
# remaining breeds are classified as NA.

breeds <- c('Golden Retriever',
 'Labrador Retriever',
 'Pembroke',
 'Chihuahua',
 'Pug')

df = within(df, {
    breed = ifelse(dog_breed %in% breeds, df$dog_breed, NA)
})
df$breed <- factor(df$breed, ordered=TRUE, levels=breeds)
```

Let me first take a look at the distribution of the ratings.

```{r, distribution rating}
ggplot(aes(x=rating_numerator), data=subset(df, df$breed != "other")) +
    geom_histogram(binwidth=1, color="white") +
    scale_x_continuous(breaks=seq(0,150,15))
```

Looks like most of the ratings are below 15 with some significant outliers. Let 
me take a look at the outliers.

```{r, rating outliers}
filter(df, rating_numerator>15) %>%
    select(rating_numerator, text)
```

Looks like a bunch of them are ratings with a decimal point. Highlighting the 
fact that not all cleanliness issues can be fixed.<br>
Though most of them are true ratings. Must be exceptionally good dogs.

Now, I want to know tweeting habits of @WeRateDogs. Let's check how much they 
tweeted over time.

```{r, tweets over time}
ggplot(aes(x=timestamp), data=df) +
    geom_density(adjust=1/8, size=1)
```

Looks like they had an exciting start! But the number of tweets gradually over 
time. I wonder if the tweeted a type of dog more than the other.

```{r, tweets over time by breed}
ggplot(aes(x=timestamp, fill=breed), data=df) +
    geom_density(adjust=1/3, position="stack") +
    scale_fill_brewer(palette="Spectral")
```

Looks like the distribution is fairly even. Pugs and Chihuahuas were the most 
common breeds at the begining, but Pugs seem to fave fallen in numbers near 
January 2017. Golden Retrievers seemed to be the most popular around that time.

Though no matter what breed, they are all good dogs. :D

<!---
Refrences: 
 https://ggplot2.tidyverse.org/reference/geom_density.html
 http://www.sthda.com/english/wiki/ggplot2-colors-how-to-change-colors-automatically-and-manually
---!>
